Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-25 manuscript.Rmd
more introduction

Wear time is not an issue. Lots of Smith and other studies with long recordings.

>>>>

Measuring infant movement with inertial movement units (IMUs) is a promising avenue for long form recordings of motor behavior in the home. Lightweight sensors (XX-XXg) can be embedded in garments to make recordings fully *mobile*, and they are *unobtrusive* because they do not require a researcher's presence nor do they record sensitive audio/video that might influence participants' behavior. Many commerically-available and inexpensive IMUs have > 12 hour battery life an onboard storage to record *real-time*, *full-day* data of movements at a sampling rate that is higher than typical video (e.g., 50-100 Hz). Moreover, past work has successfully recorded the rate of leg kicks [SMITH CITE] and activity intensity [CITES] in infants and children across an entire day.

The open question is whether *automatic classification* is sufficiently accurate to measure movement categories that are relevant to developmental and clinical research, and whether measurement validity is acceptable over long recording periods.
